\sys: Automated Data-Parallel Shell Processing

### 2020-04-07 pldi/draft.tex

\TODO{(This problem is a nice followup for the one above) Problem:
  Dataflow graph termination. Illustration: Show the example of head
  deadlock and explain that this is inherent behaviour in the shell.
  (Solution: emptying pipelines or terminating processes) In order for
  things to terminate gracefully, dish wraps all commands in order to
  always consume all of their input by sending it down to
  /dev/null. Warning: This means that all commands in the pipeline
  must terminate if all of their output is consumed. We evaluate the
  overhead of emptying all outputs in section X.}

>>>>

\TODO{(This problem is a nice followup for the one above) Problem:
  Dataflow graph termination. Illustration: Show the example of head
  deadlock and explain that this is inherent behaviour in the shell.
  (Solution: emptying pipelines or terminating processes) In order for
  things to terminate gracefully, dish wraps all commands in order to
  always consume all of their input by sending it down to
  /dev/null. Warning: This means that all commands in the pipeline
  must terminate gracefully if all of their output is consumed (if a
  process dies unexpectedly, noone will consume its input. We leave
  addressing that and other monitoring questions for future work). We
  evaluate the overhead of emptying all outputs in section X.}
